### 2016-02-08 paper.tex
Minor changes in Sec 3

{\flushleft \em Constructing the MS-PUF. }
The MS-PUF is created by connecting outputs of DAC to an
input channel of an ADC. This creates loops between the processors
cores, DACs, and ADCs as shown in Figure~\ref{fig:ms-puf}.
If there are $n$ DACs and $m$ ADCs in the device
(and $n \le m$), then $n$ such loops are made resulting in $n$ feedback channels.
The PUFs challenge is a time-series pattern comprising of
$\alpha$-bit digital values and a sequence of random channel identifiers.
The response is a time-series pattern comprising of $\beta$-bit digital 
values obtained from the ADC. The values for $\alpha$ and $\beta$ are
respectively dependent on the DAC and ADC resolutions. Typically, $\alpha = \beta$
for a device and have values 8, 12, 16, or 24.

Algorithm~\ref{algo:puf_sw} depicts the MS-PUF. 
The sofware running in the processor core 
selects the first channel from the sequence ($\mathbf L$) and 
transfers the time-series digital pattern to the corresponding
DAC one value at a time ({\em line~5}). Each digital value is converted to an analog voltage (or
current) and reconverted to a representative digital value by the ADC.
The software program reads these values from the ADC to form a new digital time-series 
pattern ({\em line~7}). This pattern forms the input to the next channel in the sequence. The process
is repeated for the entire sequence. A function $g$ processes the initial pattern ($\mathbf C$) and 
the final pattern formed (corresponding to $\mathbf L_{len(L)}$) to form the PUFs response.

@@

In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $\beta$-bit 
reply from the ADC is the result of $\alpha$-bit DAC input $\mathbf T_j$ 
undergoing a conversion to analog followed by a reconversion to digital. 
Due to reasons such as quatification and ambient noise, the result ($r$)
would be different from $\mathbf T_j$ even if $\alpha = \beta$.

Due to nano-scale variations, devices would inject certain randomness into
$r$ that would depend on the channel used and would vary from one device to another.

There are several potential reasons for variations 
between devices.
A DAC output for instance, is influenced by several nano-scale features such 
as voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have built in DACs, therefore
would be affected by the same variations as the DAC. Additionally,
other components in the ADC such as sample and hold circuits and
comparators could lead to differences in the reply.

>>>>

{\flushleft \em Constructing the MS-PUF. }
The MS-PUF is created by connecting outputs of DACs to 
input channels of an ADC. This creates loops between the processors
core, DACs, and ADCs as shown in Figure~\ref{fig:ms_puf}.
If there are $\alpha$ DACs and $\beta$ ADC channels in the device
(and $\alpha \le \beta$), then $\alpha$ such loops are made resulting 
in $\alpha$ feedback channels.
The PUFs challenge is a time-series pattern comprising of
$n$-bit digital values and a sequence of random channel identifiers.
The response is a time-series pattern comprising of $n$-bit digital 
values obtained from the ADC. The values for $n$ and $m$ are
respectively dependent on the DAC and ADC resolutions. Typically, $n = m$
for a device and have values 8, 12, 16, or 24.

Algorithm~\ref{algo:puf_sw} depicts the MS-PUF. 
The sofware running in the processor core 
selects the first channel from the sequence and 
transfers the time-series digital pattern to the corresponding
channel one value at a time ({\em line~5}). Each input is converted to an analog voltage (or
current) by the DAC and reconverted to a  digital value by the ADC.
The software program reads these values from the ADC to form a new digital time-series 
pattern ({\em line~7}). This pattern forms the input to the next channel in the sequence. The process
is repeated for the entire sequence. A function $g$ processes the initial pattern ($\mathbf C$) and 
the final pattern formed (corresponding to $\mathbf L_{len(L)}$) to form the PUFs response.

@@

In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit 
reply from the ADC is the result of the $n$-bit DAC input $\mathbf T_j$ 
undergoing a conversion to analog followed by a reconversion to digital. 
Due to reasons such as quatification and ambient noise, the result ($r$)
would be different from $\mathbf T_j$ even if $m = n$.

Due to nano-scale variations, devices would inject certain randomness into
$r$ that would depend on the channel used and would vary from one device to another. 
There are several potential reasons for variations between channels and devices.
A DAC output for instance, is influenced by several nano-scale features such 
as voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have built in DACs, therefore
would be affected by the same variations as the DAC. Additionally,
other components in the ADC such as sample and hold circuits and
comparators could lead to differences in the reply.
